\documentclass{beamer}

% Theme
\usetheme{Madrid}

% Packages
\usepackage{graphicx}
\usepackage{hyperref}

% Title Page
\title{Commit-Connect}
\author{Code Blooded}
\date{\today}

\begin{document}

% Title Slide
\begin{frame}
    \titlepage
\end{frame}

% Introduction Slide
\begin{frame}{Introduction}
    \begin{itemize}
        \item Commit-Connect is a platform that helps developers find open-source projects based on their skills.
        \item Uses GitHub API and Gemini AI to recommend repositories.
    \end{itemize}
\end{frame}

% Problem Statement
\begin{frame}{Problem Statement}
    \begin{itemize}
        \item Many developers struggle to find relevant open-source projects.
        \item Manual searching is time-consuming.
        \item Need an AI-driven approach for better recommendations.
    \end{itemize}
\end{frame}

% Features
\begin{frame}{Features}
    \begin{itemize}
        \item GitHub login with Personal Access Token authentication
        \item Fetch and display user repositories
        \item Recommend open-source projects based on interests
        \item Visualize user profile statistics
    \end{itemize}
\end{frame}

% Tech Stack
\begin{frame}{Tech Stack}
    \begin{itemize}
        \item Frontend: Streamlit
        \item Backend: Python
        \item APIs: GitHub API, Gemini AI
        
    \end{itemize}
\end{frame}

% Workflow / Methodology
\begin{frame}{Workflow}
    \begin{enumerate}
        \item User logs in using GitHub PAT
        \item Fetches repositories and languages used
        \item Queries Gemini AI for project recommendations
        \item Displays relevant repositories and issues
    \end{enumerate}
\end{frame}

% Demo
\begin{frame}{Demo}
    
\end{frame}

% Future Scope
\begin{frame}{Future Scope}
    \begin{itemize}
        \item Improve AI-based recommendations
        \item Add filtering by difficulty level
        \item Expand to other coding platforms like GitLab
    \end{itemize}
\end{frame}

% Conclusion
\begin{frame}{Conclusion}
    \begin{itemize}
        \item Commit-Connect simplifies open-source project discovery.
        \item Helps developers contribute effectively.
        \item Future improvements will enhance personalization.
    \end{itemize}
\end{frame}

\end{document}
